데이터 분석가의 R 패키지 개발 도전기

### 2021-10-10 draft.Rmd
리팩토링 내용 수정

.pull-left[
```{r, echo=TRUE, message=FALSE}
library(dmtr)
library(corrr)
library(dplyr)
binaryclass2 %>% 
  select(x1, x2) %>% 
  correlate()
```
]

.pull-right[
```{r, echo=TRUE, message=FALSE}
library(dmtr)
library(dplyr)
binaryclass2 %>% 
  select(x1, x2) %>% 
  corrr::correlate()
```

@@

  + **tidy eval** 프레임워크 활용

```r
fisher_ld <- function(.data, .group_var, .xvar) {
* .group_var <- rlang::enquo(.group_var)
* .xvar <- rlang::enquo(.xvar)
* mu_hat <- group_mean(.data, !!.group_var, !!.xvar)

  if (length(mu_hat) != 2L) {
    stop("number of levels of .group_var must be 2.")
  }

* sigma_hat <- pooled_variance(.data, !!.group_var, !!.xvar)

  res <- solve(sigma_hat) %*% purrr::reduce(mu_hat, `-`) %>% drop()
  attr(res, "group") <- attr(mu_hat, "group")
  return(res)
}

* fisher_ld(binaryclass2, class, c(x1, x2))
```

>>>>

.pull-left[
```{r, echo=TRUE, message=FALSE}
library(dmtr)
library(corrr) #<<
library(dplyr)
binaryclass2 %>% 
  select(x1, x2) %>% 
  correlate() #<<
```
]

.pull-right[
```{r, echo=TRUE, message=FALSE}
library(dmtr)
library(dplyr)
binaryclass2 %>% 
  select(x1, x2) %>% 
  corrr::correlate() #<<
```

@@

```{r rlang-logo, out.width='30%'}
knitr::include_graphics(
  "images/rlang-logo.png"
)
```
